### 2017-10-06 Gruba/01-intro.tex

The contributions of this work include:
\begin{itemize}
\item We present a system named \sys{} with the novel perspective to model user behaviors over groups instead of the mono model in literature.
\item We leverage user interests to facilitate the modeling of \retg{} behavior and look into interests with various dimensions, including long-term/recent interests and explicit/implicit interests.
\item We evaluate the performance of \sys{} using real-world datasets, showcasing its benefits against competitive state of the art approaches.
\end{itemize}

The rest of this paper is organized as follows.
Section \ref{sec:overv} first gives the problem formulation and subsequently overviews \sys{}'s components, principle of which are detailed in Sections \ref{sec:fe}, \ref{sec:uc} and \ref{sec:gm} separately.
Section \ref{sec:perf} provides the performance evaluation.
Related work is presented in Section \ref{sec:rela}.
Finally, Section \ref{sec:conclu} concludes the work.

>>>>

\stitle{Contributions.}  The contributions of this work include:

\stab(1) We present a system named \sys{} with the novel perspective to model user behaviors over groups instead of the mono model in literature.

\stab(2) We leverage user interests to facilitate the modeling of \retg{} behavior and look into interests with various dimensions, including long-term/recent interests and explicit/implicit interests.

\stab(3) We evaluate the performance of \sys{} using real-world datasets, showcasing its benefits against competitive state of the art approaches.

\stitle{Organization.} The rest of this paper is organized as follows.
Section \ref{sec:overv} first gives the problem formulation and subsequently overviews \sys{}'s components, principle of which are detailed in Sections \ref{sec:fe}, \ref{sec:uc} and \ref{sec:gm} separately.
Section \ref{sec:perf} provides the performance evaluation.
Related work is presented in Section \ref{sec:rela}.
Finally, Section \ref{sec:conclu} concludes the work.
